О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-27 pps-linear-bound/pps-linear-lower-bound.tex
Proofreading by Usachev - p. 3

For building the bound, we also require the following results and notions from~\cite{our-vmmsh-2018}.

@@

\begin{lemma}
	\label{lemma:quadr_diag_edges}
	Let $ABCD$ be a convex quadrilateral on the plane.
	Then $\max\{AC,BD\}>\min\{AB,BC,CD,DA\}$,
	i.e. at least one diagonal is greater than at least one side.
\end{lemma}

>>>>

To prove the bound on $d(2,n)$, we also need the following results and notions from~\cite{our-vmmsh-2018}.

@@

\begin{lemma}
	\label{lemma:quadr_diag_edges}
	Let $ABCD$ be a convex quadrilateral on the plane.
	Then $\max\{AC,BD\}>\min\{AB,BC,CD,DA\}$,
	that is at least one diagonal is greater than at least one side.
\end{lemma}
